Reading the Titanic data set into R.  Create a dataframe called "Titanic". 
```{r}
setwd("C:/Users/vaibhav/Desktop")
Titanic.df<-read.csv("TitanicData.csv")
View(Titanic.df)
```
Using R to count the total number of passengers on board the Titanic.
```{r}
dim(Titanic.df)
```
Using R to count the number of passengers who survived the sinking of the Titanic.
```{r}
my.table<-with(Titanic.df,table(Survived))
my.table
```
Using R to measure the percentage of passengers who survived the sinking of the Titanic.
```{r}
prop.table(my.table)*100
```
Using R to count the number of first-class passengers who survived the sinking of the Titanic.
```{r}
my.table<-xtabs(~ Survived+Pclass,data=Titanic.df)
my.table
        
```
Using R to measure the percentage of first-class passengers who survived the sinking of the Titanic. 
```{r}
prop.table(my.table,2)*100
```
Using R to count the number of females from First-Class who survived the sinking of the Titanic
```{r}
my.table<-xtabs(~Pclass+Survived+Sex,data=Titanic.df)
ftable(my.table)
```
Using R to measure the percentage of survivors who were female
```{r}
my.table<-xtabs(~Survived+Sex,data=Titanic.df)
my.table
prop.table(my.table,1)*100
```
Using R to measure the percentage of females on board the Titanic who survived
```{r}
my.table<-xtabs(~Survived+Sex,data=Titanic.df)
my.table
prop.table(my.table,2)*100
```
Runnig a Pearson's Chi-squared test to test the following hypothesis:

Hypothesis:  The proportion of females onboard who survived the sinking of the Titanic was higher than the proportion of males onboard who survived the sinking of the Titanic.

```{r}
chisq.test(my.table)

```

